### 2019-09-14 2019_neurips_vigil/intro.tex
intro

Starting with the Visual Question Answering (VQA) dataset \cite{}, many tasks that integrate vision and language have emerged in the past several years\cite{mogadala2019trends}.  As a departure from the simpler vision tasks like classification and object detection, visual reasoning has become the core emphasis in these tasks. Visual reasoning mainly deals with the comparison of object attributes, counting and other relational questions.

>>>>

Starting with the Visual Question Answering (VQA) dataset \cite{}, a variety of tasks that integrate vision and language have emerged in the past several years\cite{mogadala2019trends}.  As a departure from the simpler vision problems like classification and object detection, visual reasoning has become the core emphasis in these tasks. Visual reasoning mainly deals with the comparison of object attributes, counting and other relational questions.
